data wrangling and plots

### 2021-03-16 shared analysis files /data_wrangling_plot8march.Rmd
changing the contour plot to excluded big negative yi

```{r}
#contour plot with flux_range on the x axis, mean temp of the y axis and colored by yi
fig <- plot_ly(
  x = dat_MA_ES$flux_range, 
  y = dat_MA_ES$mean_temp_constant, 
  z = dat_MA_ES$yi, 
  type = "contour" 
)

>>>>

```{r}
#contour plot with flux_range on the x axis, mean temp of the y axis and colored by yi
fig <- plot_ly(
  x = normalized$flux_range, 
  y = normalized$mean_temp_constant, 
  z = normalized$yi, 
  type = "contour")
fig
